---
title: Measuring effect through experimenting
author: "András Bérczi"
date: "October 9, 2019"
output: html_document
# runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr::opts_knit$set(root.dir = '..')
```

```{r}
suppressPackageStartupMessages(library(data.table))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(magrittr))
suppressPackageStartupMessages(library(lubridate))
```

# 1. Calculate the Minimum Detectable Effect for a sample of 1000 contacts, when the base rate is 10%. Use the `calculateMinimumDetectableEffect` function!

```{r function to calculate the Minimum Detectable Effect}
calculateMinimumDetectableEffect <- function(p1, n, prop_of_treatment = 0.5, alpha = 0.05, beta = 0.2) {
    M <- qt(1-alpha/2, n - 1) + qt(1-beta, n - 1)
    variance <- p1 * (1 - p1)
    weight <- prop_of_treatment * (1 - prop_of_treatment) * n
    M * sqrt(variance / weight)
}
# solution:
calculateMinimumDetectableEffect(0.1, 1000)
```

# 2. Calculate the effect for the whole period of the [provided example experiment](./experiment_result.csv)

```{r}
data <- fread("data/experiment_result.csv")

dt <- data[, .(num_open = sum(did_open), num_send = .N), by = group] %>%
  .[, .(group, open_rate = num_open/num_send)]

dt[group == "treatment", open_rate] / dt[group == "control", open_rate]

# own solution

# treatment_opened = count(data, (group == "treatment" & did_open == 1))
# treatment_total = count(data, group == "treatment")
# control_opened = count(data, (group == "control" & did_open == 1))
# control_total = count(data, group == "control")
# uplift = round((treatment_opened[[2]][[2]]/treatment_total[[2]][[2]])/
#   (control_opened[[2]][[2]]/control_total[[2]][[2]])-1, digits = 2)
```

# 3. Plot the results

```{r}
ggplot(dt, aes(x = group, y = open_rate)) + geom_col() +
  labs(title = "Open rate for all period") + xlab("Open rate")
```

# 4. Calculate the effect week-by-week
# 5. Plot the results

```{r}
data[, send_week := floor_date(as.Date(send_date), unit = "week", week_start = 1)]
dt_week <- data[, .(num_open = sum(did_open), num_send = .N), by = .(group, send_week)] %>%
  .[, .(group, send_week, open_rate = num_open / num_send)]

effect_dt <- dcast(dt_week, send_week ~ group) %>%
  .[, .(send_week, uplift = treatment / control)]

ggplot(effect_dt, aes(x = send_week, y = uplift)) + geom_line()

# own solution

# dt2 <- data[, no_week := (((as.numeric(rownames(data)) - 1) %/% 7) + 1) %% 8]
# dt2 <- dt2[no_week == 0, no_week := 8]
# 
# # copied from here
# dt2_week <- data[, .(num_open = sum(did_open), num_send = .N), by = .(group, no_week)] %>%
#   .[, .(group, no_week, open_rate = num_open / num_send)]
# effect_dt2 <- dcast(dt2_week, no_week ~ group) %>%
#   .[, .(no_week, uplift = treatment / control)]
# ggplot(effect_dt2, aes(x = no_week, y = uplift)) + geom_line()

```

# 6. How would you plot uncertainty? Try to do it for both plots!